% =============================================================================
% CareerForge Cover Letter Template
% Class:   cfcl.cls  (CareerForge Cover Letter class)
% Compile: xelatex main_example.tex    (run from cover_letters/ directory!)
% Output:  main_example.pdf            (target: 1 page)
%
% Generated copies: cover_letters/main_<Company>_<Role>.tex  (gitignored)
% Tokens:  Fields marked  % {{TOKEN_NAME}}  are replaced by the AI skill.
%          See .claude/skills/job-application-assistant/06-cover-letter-templates.md
%
% IMPORTANT: Always compile from cover_letters/ so font paths resolve correctly.
%   cd cover_letters && xelatex main_example.tex
% =============================================================================

\documentclass{cfcl}

\begin{document}

% ── Header ────────────────────────────────────────────────────────────────────
\clname{Jane Smith}                                           % {{CANDIDATE_NAME}}
\smallskip
\cltagline{Machine Learning Engineer · Python Developer}      % {{TAGLINE}}
\smallskip
\primarycontact{%
  \citem{\faEnvelope}{\href{mailto:jane.smith@email.com}{jane.smith@email.com}}\quad  % {{EMAIL}}
  \citem{\faPhone}{+1 (415) 555-0198}\quad                                             % {{PHONE}}
  \citem{\faLinkedinIn}{\href{https://linkedin.com/in/janesmith}{linkedin.com/in/janesmith}}% {{LINKEDIN}}
}
\smallskip
\secondarycontact{%
  \citem{\faLocationDot}{San Francisco, CA}\quad                                        % {{LOCATION}}
  \citem{\faGithub}{\href{https://github.com/janesmith}{github.com/janesmith}}\quad    % {{GITHUB}}
  \citem{\faGlobe}{\href{https://janesmith.dev}{janesmith.dev}}                         % {{PORTFOLIO}}
}
\clheadrule

% ── Recipient + Date ──────────────────────────────────────────────────────────
\recipient{Anthropic, Inc.}{548 Market St, Suite 28220}{San Francisco, CA 94104, USA}  % {{RECIPIENT_*}}
\letterdate{June 7, 2026}                                                               % {{DATE}}

% ── Subject ───────────────────────────────────────────────────────────────────
\clsection{Re: Senior Machine Learning Engineer}              % {{ROLE_TITLE}}

% ── Opening ───────────────────────────────────────────────────────────────────
\opening{Dear Hiring Manager,}                                % {{SALUTATION}}

% Paragraph 1: Who you are + why you are applying.            % {{INTRO_PARA}}
I am writing to express my interest in the Senior Machine Learning Engineer
position at Anthropic. With five years of hands-on experience building
production ML systems in Python and a track record of shipping models that
directly improve user outcomes, I am confident I can contribute meaningfully
from day one.

% Paragraph 2: Concrete evidence of skills matching the job.  % {{BODY_PARA_1}}
At TechStart Inc., I led the end-to-end delivery of a real-time recommendation
engine that increased click-through rates by 23\% within three months of
deployment. The system processes over two million events per day using PyTorch,
with a custom feature store backed by Redis and PostgreSQL.

% Paragraph 3: Company-specific hook showing genuine research. % {{BODY_PARA_2}}
What draws me to Anthropic is your commitment to safety-first AI development.
Your recent work on constitutional AI aligns directly with research I have
been pursuing independently, and I would welcome the chance to bring that
perspective to a team that treats rigour as a first-class concern.

% ── Closing ───────────────────────────────────────────────────────────────────
\closing{%
  I look forward to discussing how my experience can support Anthropic's mission.
  Thank you for your time and consideration.%      % {{CLOSING}}
}{Jane Smith}                                      % {{CANDIDATE_NAME}}

\vfill
\noindent\textcolor{accent}{\rule{\linewidth}{1.2pt}}

\end{document}
