% =============================================================================
% CareerForge CV Template — Single Column (ATS-optimised)
% Class:   cfcv.cls
% Compile: lualatex main_example.tex    (run from cv/ directory)
% Output:  main_example.pdf             (target: 1 page)
%
% ATS notes:
%   - No letter-spacing on name, titles, or section headers
%   - Skills listed as plain text (not tikz graphics)
%   - Standard section names understood by all major ATS
%   - No \project{} block — ATS reads company + role + bullets cleanly
%
% Tokens:  Fields marked  % {{TOKEN}}  are replaced by the AI /apply skill.
%          See .claude/skills/job-application-assistant/05-cv-templates.md
% =============================================================================

\documentclass[10pt, a4paper]{cfcv}
\geometry{left=1.2cm,right=1.2cm,top=1.2cm,bottom=1.2cm}
\usepackage[default]{lato}
\usepackage{multicol}
\usepackage{hyperref}

\begin{document}

% ── Header ────────────────────────────────────────────────────────────────────
\name{Jane Smith}                                          % {{CANDIDATE_NAME}}
\tagline{ML Engineer · Python Developer}                   % {{TAGLINE}}
\personalinfo{%
  \mailaddress{jane.smith@email.com}                       % {{EMAIL}}
  \phone{+1 (415) 555-0198}                               % {{PHONE}}
  \linkedin{linkedin.com/in/janesmith}{https://linkedin.com/in/janesmith}  % {{LINKEDIN}}
  \github{github.com/janesmith}{https://github.com/janesmith}             % {{GITHUB}}
  \location{San Francisco, CA}                             % {{LOCATION}}
}
\makecvheader

% ── Summary ───────────────────────────────────────────────────────────────────
\cvsection{Summary}
Software engineer with five years of experience building production ML systems
in Python. Proven track record of delivering data-driven products that move
business metrics. Passionate about clean architecture and team collaboration.
% {{PROFESSIONAL_SUMMARY}}

% ── Experience ────────────────────────────────────────────────────────────────
\cvsection{Professional Experience}

\company{TechStart Inc.}{ML Engineer}{San Francisco, CA}{Jan 2022 – Present}
% {{COMPANY_1_*}}
Brief company description — what the company does and your role within the team.
% {{COMPANY_1_DESCRIPTION}}
\begin{itemize}
  \item Delivered real-time recommendation engine that increased CTR by 23\% within 3 months of deployment, processing 2M+ events/day via PyTorch and Redis.  % {{ACHIEVEMENT_1}}
  \item Collaborated with infrastructure team to meet <100ms p99 latency SLA; reduced incident rate by 40\% through improved monitoring.                         % {{ACHIEVEMENT_2}}
\end{itemize}

\divider

\company{PrevCorp}{Junior Software Developer}{New York, NY}{Jun 2019 – Dec 2021}
% {{COMPANY_2_*}}
Brief description of second role and the team context.
% {{COMPANY_2_DESCRIPTION}}
\begin{itemize}
  \item Built internal analytics dashboard that reduced manual report generation time by 60\%, adopted across three business units.                                % {{ACHIEVEMENT_3}}
  \item Maintained and extended REST APIs serving 500K daily active users with 99.9\% uptime over 18 months.                                                     % {{ACHIEVEMENT_4}}
\end{itemize}

% ── Skills ────────────────────────────────────────────────────────────────────
\cvsection{Skills}
\skillset{Programming}{Python, JavaScript, TypeScript, Bash, SQL}          % {{SKILL_PROGRAMMING}}
\skillset{Machine Learning}{PyTorch, TensorFlow, scikit-learn, MLflow, Hugging Face}  % {{SKILL_ML}}
\skillset{Infrastructure}{Docker, Kubernetes, AWS, GCP, PostgreSQL, Redis} % {{SKILL_INFRA}}

% ── Certifications ────────────────────────────────────────────────────────────
\cvsection{Certifications}
\cvachievement{\certificatesymbol}
  {AWS Certified Machine Learning – Specialty}             % {{CERT_1_NAME}}
  {March 2024}                                             % {{CERT_1_DATE}}
  {Professional certification for designing and deploying ML solutions on AWS.}
% {{CERT_1_DESC}}
\par\smallskip
\button{\href{https://example.com/cert}{{\color{accent}\linksymbol}\hspace{0.4em}Verify}}
% {{CERT_1_URL}}

% ── Education + Languages ─────────────────────────────────────────────────────
\begin{multicols}{2}
  \cvsection{Education}
  \education
    {M.Sc. Computer Science}     % {{DEGREE}}
    {Stanford University}        % {{UNIVERSITY}}
    {Palo Alto, CA}              % {{UNI_LOCATION}}
    {2017 – 2019}                % {{EDU_DATE_RANGE}}

  \columnbreak

  \cvsection{Languages}
  \begin{itemize}
    \item English – Native       % {{LANGUAGE_1}}
    \item Spanish – B2           % {{LANGUAGE_2}}
  \end{itemize}
\end{multicols}

\end{document}
